### 2013-05-01 inst/examples/BUGS/parametric-vs-nonparametric.Rmd
run means example as separate script

```{r}
MaxT = 1000
# uses expected values from GP, instead of integrating over posterior
# matrices_gp <- gp_transition_matrix(gp_dat$E_Ef, gp_dat$E_Vf, x_grid, h_grid)

# Integrate over posteriors 
matrices_gp <- gp_transition_matrix(gp_dat$Ef_posterior, gp_dat$Vf_posterior, x_grid, h_grid)

>>>>

```{r}
MaxT = 1000
# uses expected values from GP, instead of integrating over posterior
matrices_gp <- gp_transition_matrix(gp_dat$E_Ef, gp_dat$E_Vf, x_grid, h_grid)

# Integrate over posteriors 
#matrices_gp <- gp_transition_matrix(gp_dat$Ef_posterior, gp_dat$Vf_posterior, x_grid, h_grid)
